---
title: "Exercise: Explore, Clean, and Wrangle Data"
author: "Pascale"
format: html
---

## Data
Data on abundance, size and fishing pressure of California spiny lobster (Panulirus interruptus) are collected along the mainland coast of the Santa Barbara Channel. This dataset contains two tables. 1) Abundance and size data collected annually by divers in late summer before the start of the fishing season at five SBC LTER long term kelp forest study sites, and 2) Fishing pressure, as determined by counting the number of commercial trap floats. Data are collected every two to four weeks during the lobster fishing season (October to March) at nine sites along the mainland.

## Setup
```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
```


## Read and explore data
```{r}

# Read in data
lobster_abundance <- read_csv("https://portal.edirepository.org/nis/dataviewer?packageid=knb-lter-sbc.77.8&entityid=f32823fba432f58f66c06b589b7efac6")

lobster_traps <- read_csv("https://portal.edirepository.org/nis/dataviewer?packageid=knb-lter-sbc.77.8&entityid=66dd61c75bda17c23a3bce458c56ed84")

```
```{r}
head(lobster_abundance)

head(lobster_traps)

str(lobster_abundance)

str(lobster_traps)

summary(lobster_abundance)

summary(lobster_traps)
```

## Exercise 1
Problem: The variable SIZE_MM uses -99999 as the code for missing values (see metadata). 

GOAL: (1) Verify the SIZE_MM variable contains -99999 values using unique().(2) Convert every -99999 value to an NA value using mutate() and na_if(). Look up the help page to see how to use na_if(). (3)Check your output data using unique().)

```{r}
unique(lobster_abundance$SIZE_MM)
```
```{r}
abundance_clean <- lobster_abundance %>%
    mutate(SIZE_MM = if_else(condition = SIZE_MM == -99999.0, 
                             true = NA, 
                             false = SIZE_MM))

abundance_clean_2 <- lobster_abundance %>%
    mutate(SIZE_MM = na_if(SIZE_MM, -99999.0))

unique(abundance_clean$SIZE_MM)
```


## Exercise 2 

GOAL: Create a subset with the data for the lobsters at Arroyo Quemado (AQUE) that have a carapace length greater than 70 mm.

```{r}
subset <- lobster_abundance %>% 
  filter(SITE == "AQUE" & SIZE_MM > 70)
```

## Exercise 3 
GOAL: Create a subset with the traps’ information at all sites where abundance data is not NA. Note that you first have to identify which are these sites.

```{r}
site <- setdiff(lobster_traps$SITE, lobster_abundance$SITE) 

subset_ex_3 <- lobster_abundance %>% 
  filter(SITE, -"ABUR", "AHND", "GOLB", "AHND to AQUE", "AHND TO AQUE") %>% 
  filter(COUNT !is.na())

```

## Exercise 4 
GOAL: Calculate totals by site and year
```{r}
lobster_abundance %>% 
  group_by(SITE, YEAR) %>% 
  summarise(catch_sum = sum(COUNT))
```

## Exercise 5 
GOAL: Joining two data frames
```{r}

```

## Exercise 6
GOAL: Adding a new column
```{r}

```

